\textbf{Linear Algebra}\\A summary for MIT 18.06SC

### 2020-06-30 skills/math/linear_algebra_summary.tex

	Consider the RREF form of $\mA$, $\mR = RREF(\mA)$. There are elimination matrix $\mE$ and permutation matrix $\mP$ such that
	\[ \mE \mP \mA =  \mR. \]
	By the full rankness of $\mA$,  $\mA$ has $n$ pivot columns, and thus $\mR = \mI_n$. By lemma \ref{lem:elim}, $\mE$ is invertible. The permutation matrix $\mP$ is also invertible. Then, the matrix product $\mE \mP$ is invertible and $\mA$ is the inverse of $\mE \mP$. Therefore, $\mA$ is invertible.

@@

Suppose there is a solution $x = (x_1, x_2) \in N(\mA)$, where $x_1 \in \bbR^{r}$ and $x_2 \in \bbR^{n-r}$. We have 
\begin{align}
	\mR x = \begin{bmatrix} \mI_r & \mF \\ 0 & 0	\end{bmatrix} \begin{bmatrix} x_1 \\ x_2	\end{bmatrix} = \begin{bmatrix} x_1 + \mF x_2 \\  0 &\end{bmatrix} = 0.
\end{align}
That implies $x_1  = -\mF x_2$ and $x = \begin{bmatrix} x_1 \\ x_2	\end{bmatrix} = \begin{bmatrix} -\mF \\ \mI_{n-r}	\end{bmatrix} x_2 = \mX x_2$. Any vector  in $ N(\mA)$ is a linear combination of special solutions, i.e. $C(\mX) = N(\mA)$. Therefore, the rank of nullspace is $rank(N(\mA)) = dim(C(\mX)) = n-r$.
\end{proof}

Recall the definitions of pivot column and free column. In $\mA x = b$, the variables in $x$ that correspond to pivot columns are called \textit{pivot variables} and others are \textit{free variables}. If $rank(\mA) = r$, there are $n-r$ free variables, which coincides with $rank(N(\mA))$.

>>>>

	Consider the RREF form of $\mA$, $\mR = RREF(\mA)$. There are elimination matrix $\mE$ and permutation matrix $\mP$ such that
	\[ \mE \mP \mA =  \mR. \]
	By the full rankness of $\mA$,  $\mA$ has $n$ pivot columns, and thus $\mR = \mI_n$. By lemma \ref{lem:elim}, $\mE$ is invertible. The permutation matrix $\mP$ is also invertible. Then, the matrix product $\mE \mP$ is invertible, and $\mA$ is the inverse of $\mE \mP$. Therefore, $\mA$ is invertible.

@@

Suppose there is a solution $x = (x_1, x_2) \in N(\mA)$, where $x_1 \in \bbR^{r}$ and $x_2 \in \bbR^{n-r}$. We have 
\begin{align}
	\mR x = \begin{bmatrix} \mI_r & \mF \\ 0 & 0	\end{bmatrix} \begin{bmatrix} x_1 \\ x_2	\end{bmatrix} = \begin{bmatrix} x_1 + \mF x_2 \\  0 &\end{bmatrix} = 0.
\end{align}
That implies $x_1  = -\mF x_2$, and $x = \begin{bmatrix} x_1 \\ x_2	\end{bmatrix} = \begin{bmatrix} -\mF \\ \mI_{n-r}	\end{bmatrix} x_2 = \mX x_2$. Any vector  in $ N(\mA)$ is a linear combination of special solutions, i.e. $C(\mX) = N(\mA)$. Therefore, the rank of nullspace is $rank(N(\mA)) = dim(C(\mX)) = n-r$.
\end{proof}

Recall the definitions of pivot column and free column. In $\mA x = b$, the variables in $x$ that correspond to pivot columns are called \textit{pivot variables}, and others are \textit{free variables}. If $rank(\mA) = r$, there are $n-r$ free variables, which coincides with $rank(N(\mA))$.
